A Case Study in Paraphrase Targeting Writing Styles

### 2012-09-01 paper/paper_weichange.tex

%% Example of a LaTeX source file for a COLING-2012 submission
%% last updated: July 10, 2012
%% Optional instructions for authors within the tex file are provided as comments and start with 'for authors:...'
\documentclass[10pt,a5paper,twoside]{article}
\usepackage{coling2012}
\usepackage{comment}
\usepackage{amsmath}
%\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
%\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{A rose would smell just as good even if it had a different name (``A rose by any other name would smell as sweet'') \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{“Be super careful on March 15” (“Beware the ides of March”) \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
%for authors: in case of more than four author names ref. to commented line below 
%\author{$Annie~SMITH^{1, 2}~~~LI~Xiao Dong^{1, 3}$\\$~~~Third~Author^{1, 2}~~~Fourth~Author^{1, 3}~~~ Fifth~Author^{2, 3}$\\
\title{Paraphrasing for Style}
\author{$Author1^{1, 2}~~~Author2^{1, 3}$\\
{\small  	(1) INSTITUTE\_1, address 1\\ 
 		(2) INSTITUTE\_2, address 2\\
		(3) INSTITUTE\_3, address 3\\
  \texttt{author1@institute1, author@institute2} \\ 
}}

\begin{document}
\maketitle
%% The first mandatory ABSTRACT (\abstractEn) section below is for the English language
\abstractEn{  %ABSTRACT}{
We present initial investigation into the task of paraphrasing language while targeting a particular writing style.
The plays of William Shakespeare and their modern translations are used as a testbed for evaluating
paraphrase systems targeting a specific style of writing.
%We demonstrate that existing evaluation metrics developed in the Machine Translation and Paraphrase communities are
%insufficient when the goal is to generate paraphrases targeting a specific style, and
%propose a series of new metrics to measure how closely the generated paraphrases match the target
%style.  
We show that even with a relatively small amount of parallel training data, it is
possible to learn paraphrase models which capture stylistic phenomena, and these models outperform
baselines based on dictionaries and out-of-domain parallel text.
In addition we present an initial investigation into automatic evaluation metrics for paraphrasing writing style.
To the best of our knowledge this is the first work to investigate the task of
paraphrasing text with the goal of targeting a specific style of writing.
}

@@

The same meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.

Paraphrases can differ along many dimensions, including utterance length, diction level, and speech register. 
There is a significant literature in sentence compression aimed at modeling the first of these, length: 
producing meaning-preserving alternations that reduce the length of the input string \cite{Chandrasekar96,Vanderwende07,Yatskar10}.
However, we know of no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
Can we learn to reliably map from one form of language to another, transforming formal prose into a more colloquial form, or a casual email into a more formal equivalent?

@@

Systems capable of paraphrasing text targeting a specific writing style could be useful for a variety of applications.  For example, they could:
\begin{enumerate}
  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
  \item Enable average people to better consume information by translating legalese or medical jargon into nontechnical English.  
  \item Benefit educational applications, allowing students to:
    \begin{enumerate}
    \item Access \emph{modern English} versions of works by authors they are studying.
    \item Experiment with writing in the style of an author they are studying.
    \end{enumerate}
\end{enumerate}

@@

We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation (MT) and Paraphrase literature, however no previous work has investigated the ability of automatic
evaluation metrics to capture the notion of writing style.  
We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and 
show that these metrics correlate well with human judgments.

@@

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table extracted from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, again excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT}. \\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 plays with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model.\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
      in detail in \S \ref{video_baseline}. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in \S \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakespearean paraphrase.  {\em Romeo and Juliet} is held out for testing.}
  \label{systems}
\end{table}

@@

\subsection{Language Model Style Metric}
Another approach is to build seperate language models for text in the target style and outside the style, and apply Bayes' rule to estimate
the probability that a particular sentence was generated based on the style or not:
\begin{eqnarray*}
P(\text{style}=\text{target}|\text{sentence}) 
& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) P(\text{target})}{P(\text{sentence})} \\
& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5}{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5 + P_\text{LM}(\text{sentence}|\text{source}) \times 0.5} \\
& = & \frac{P_\text{LM}(\text{sentence}|\text{target})}{P_\text{LM}(\text{sentence}|\text{target}) + P_\text{LM}(\text{sentence}|\text{source})} \\
\end{eqnarray*}

That is the probability that a sentence was generated according to the target style is simply it's probability according to the target language model divided by the sum of it's
probability according to the source and target language models.

@@

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|r|r|}
    \hline
    & & $\rho$ (Annotator 1) & $\rho$ (Annotator 2) \\
    \hline
    \hline
    semantic adequacy & BLEU & 0.35 & 0.31 \\
    \hline
    dissimilarity & PINC & 0.78 & 0.82 \\
    \hline
    style & BLEU & 0.07 & 0.06 \\
    \hline
    style & PINC & 0.20 & 0.45 \\
    \hline
    style & Cosine & 0.37 & 0.41 \\
    \hline
    style & LM & 0.45 & 0.48 \\
    \hline
    style & Logistic regression & 0.47 & 0.47 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Correlation between various human judgments and automatic evaluation metrics.  Pearson's correlation coefficient is displayed
  between the automatic metrics and human judgements from each annotator.}
  \label{correlation}
\end{table}

@@

Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.

We have shown that access to even a small amount of parallel text produces paraphrase systems 
capable of generating a large number of stylistically appropriate paraphrases which preserving the meaning of the input text.  
Our paraphrase systems targeting Shakesperean English could be benefical for educational applications, for example helping to
make Shakespeare's work accessable to a broader audience.
Future work could investigate stylistic paraphrasing in other domains, such as paraphrasing emails into formal documents, or
translating legal documents into nontechnical English. 
%We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
%of Shakespeare and also to human translators.

>>>>

%% Example of a LaTeX source file for a COLING-2012 submission
%% last updated: July 10, 2012
%% Optional instructions for authors within the tex file are provided as comments and start with 'for authors:...'
\documentclass[10pt,a5paper,twoside]{article}
\usepackage{coling2012}
\usepackage{comment}
\usepackage{amsmath}
%\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
%\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{A rose would smell just as good even if it had a different name (``A rose by any other name would smell as sweet'') \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{“Be super careful on March 15” (“Beware the ides of March”) \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
\title{A Case Study in Paraphrase Targeting Writing Styles}
%for authors: in case of more than four author names ref. to commented line below 
%\author{$Annie~SMITH^{1, 2}~~~LI~Xiao Dong^{1, 3}$\\$~~~Third~Author^{1, 2}~~~Fourth~Author^{1, 3}~~~ Fifth~Author^{2, 3}$\\
\author{$Author1^{1, 2}~~~Author2^{1, 3}$\\
{\small  	(1) INSTITUTE\_1, address 1\\ 
 		(2) INSTITUTE\_2, address 2\\
		(3) INSTITUTE\_3, address 3\\
  \texttt{author1@institute1, author@institute2} \\ 
}}

\begin{document}
\maketitle
%% The first mandatory ABSTRACT (\abstractEn) section below is for the English language
\abstractEn{  %ABSTRACT}{
We present initial investigation into the task of paraphrasing language while targeting a particular writing style.
The plays of William Shakespeare and their modern translations are used as a testbed for evaluating
paraphrase systems targeting a specific style of writing.
%We demonstrate that existing evaluation metrics developed in the Machine Translation and Paraphrase communities are
%insufficient when the goal is to generate paraphrases targeting a specific style, and
%propose a series of new metrics to measure how closely the generated paraphrases match the target
%style.  
We show that even with a relatively small amount of parallel training data, it is
possible to learn paraphrase models which capture stylistic phenomea, and these models outperform
baselines based on dictionaries and monolingual corpora.
In addition we present an initial investigation into automatic evaluation metrics for paraphrasing writing style.
To the best of our knowledge this is the first work to investigate the task of
paraphrasing text with the goal of targeting a specific style of writing.
}

@@

The same meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
fundamental to many natural language understanding tasks \cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.

Paraphrases can differ along many dimensions, including utterance length, diction level, and speech register. 
There is a significant literature in sentence compression aimed at modeling the first of these, length: 
producing meaning-preserving alternations that reduce the length of the input string \cite{Knight02}.
However, no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
Can we learn to reliably map from one form of language to another, transforming formal prose into a more colloquial form, or a casual email into a more formal equivalent?

@@

Systems capable of paraphrasing text targeting a specific writing style could be useful for a variety of applications.  For example, they could:
\begin{enumerate}
  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.
  \item Enable non-specialists to better consume information by translating legalese or medical jargon into nontechnical English.  
  \item Benefit educational applications, allowing students to:
    \begin{enumerate}
    \item Access \emph{modern English} versions of works by authors they are studying.
    \item Experiment with writing in the style of an author they are studying.
    \end{enumerate}
\end{enumerate}

@@

We evaluate these models both by human judges and by standard automated metrics from the Machine Translation (MT) and Paraphrase literature. However, we show that these previously proposed automatic metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
targeting a specific style of writing.  No previous work has investigated the ability of automatic
evaluation metrics to capture the notion of writing style.  We therefore propose three new automated metrics for evaluating paraphrases targeting a specific style, and 
show that these metrics correlate well with human judgments.

@@

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|p{3.5in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table is extracted from the parallel texts of 16 plays from Sparknotes plus 7 plays from Enotes. Language model is built from all 36 of Shakespeare's plays except R\&J. Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT}. \\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 plays with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model.\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
      in detail in \S \ref{video_baseline}. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in \S \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakespearean paraphrase.  {\em Romeo and Juliet} is held out for testing.}
  \label{systems}
\end{table}

@@

@@

\subsection{Language Model Style Metric}
\emph{TO ADD}

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|r|}
    \hline
    & & Pearson's $\rho$ \\
    \hline
    \hline
    semantic adequacy & BLEU & 0.35 \\
    \hline
    dissimilarity & PINC & 0.78 \\
    \hline
    style & BLEU & 0.07 \\
    \hline
    style & PINC & 0.20 \\
    \hline
    style & Cosine & 0.37 \\
    \hline
    style & Logistic regression & 0.47 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Correlation between various human judgments and automatic evaluation metrics}
  \label{correlation}
\end{table}

@@

Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.
%We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
%of Shakespeare and also to human translators.
